Increased Education Level of Women Associates with Higher Occupational Prestige and Happiness

### 2023-03-16 outputs/paper/paper.qmd
edited cross references

In this paper, the analysis will be carried out using the statistical programming language `R` [@citeR], using the `haven` \@[@citeHaven] and `tidyverse` [@citeTidy] packages. All figures in the report are generated using `ggplot2`.

>>>>

In this paper, the analysis will be carried out using the statistical programming language `R` [@citeR], using the `haven` [@citeHaven] and `tidyverse` [@citeTidy] packages. All figures in the report are generated using `ggplot2` [@citeGG].
